---
title: "STAC51 RMarkdown Tutorial"
author: "Lehang Zhong"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
  html_document: default
header-includes:
- \usepackage{subfig}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```


## Section 1

Hello World
  
*Hello World*

**Hello World**

### S1 Subsection 1

This is a math equation $a^2 + b^2 = c^2$

Likelihood function of $Bin(n,\pi)$ : $\ell(\pi \mid y)=\left(\begin{array}{l}n \\ y\end{array}\right) \pi^{y}(1-\pi)^{n-y}$

`$..$` is a inline math mode.

This is a score CI:

$$
\begin{array}{c}
\hat{\pi}\left(\frac{n}{n+z_{\alpha / 2}^{2}}\right)+\frac{1}{2}\left(\frac{z_{\alpha / 2}^{2}}{n+z_{\alpha / 2}^{2}}\right) \pm \\
z_{\alpha / 2} \sqrt{\frac{1}{n+z_{\alpha / 2}^{2}}\left[\hat{\pi}(1-\hat{\pi}) \frac{n}{n+z_{\alpha / 2}^{2}}+\frac{1}{4}\left(\frac{z_{\alpha / 2}^{2}}{n+z_{\alpha / 2}^{2}}\right)\right]}
\end{array}
$$
## Code chunks
```{r chunk1}
dbinom(0:5, 5, p=1/4)
```

### `echo = F`

```{r,echo=F}
dbinom(0:5, 5, p=1/4)
```


### `include = F`
```{r,include=F}
p1 <- dbinom(0:5, 5, p=1/4)
```

```{r eval=FALSE, include=FALSE}
p1
```

## Code Chunks with figures

```{r,echo=T}
par(mfrow=c(2,2))
plot(0:5, p1, type="h", xlab="y",
     ylab="P(y)",col="red", lwd=2)
plot(0:100, dbinom(0:100, 100, 1/4), type="h", xlab="y",
     ylab="P(y)", col="red", lwd=2)
pbinom(2, 5, 1/4)
```

## Simple way of attaching figure

## More figure code chunk options
```{r p31,echo=FALSE,fig.cap= "This is a figure caption.", out.width='0.95\\textwidth',fig.align='center'}
plot(0:100, dbinom(0:100, 100, 1/4), type="h", xlab="y",
     ylab="P(y)", col="red", lwd=2)
```

## Muliple figures with captions
```{r, fig.cap='Combine multiple plots with subcaptions', fig.subcap=c('Ff1','Ff2','Ff3','Ff4'), fig.ncol = 2, out.width = "55%", fig.align = 'center'}
plot(0:5, dbinom(0:5, 5, 1/4), type="h", xlab="y",
     ylab="P(y)",col="red", lwd=2)
plot(0:100, dbinom(0:100, 100, 1/4), type="h", xlab="y",
     ylab="P(y)", col="red", lwd=2)
plot(cars, pch = 19)
boxplot(Sepal.Width ~ Species, data = iris)
```

## Tables

```{r,out.width='0.5\\textwidth'}
library(binom)
knitr::kable(binom.confint(x=4, n=400, conf.level=.95, methods =c("ac","wilson", "lrt","exact")),
             format="latex",digits=4,caption = 'Example from Lec3 page 10')
```



